%!TEX root = icwsm2016.tex

Social media sources such as Twitter represent a massively distributed
social sensor of a \eat{rich underlying topic space}\rev{kaleidoscope of topics} ranging from social and
political events to entertainment and sports news.  \eat{However, given the
continual evolution of social media content, querying for content from
individual users or containing certain keywords or hashtags is often
insufficient to retrieve the vast range of topical content available.}
\rev{We note, however, that due to the overwhelming volume of content, 
it can be difficult to spot novel and significant topics within a broad theme 
in a timely fashion -- 
such as \#obamacare or a recent \#twochild policy in China. }
\rev{This paper propose a scalable and practical method to automatically construct social sensors for generic topics.}\eat{To automate generic social sensor construction,} we
%address the task of automatically learning topical
%social sensors that generalize to future unseen content
%As a simple
%but critical insight, we leverage hashtags as proxies for topical
%content to automatically label a vast corpus of social media with only
%a small number of topical hashtags that users can easily curate.  With
%this labeled data in hand, we train a supervised learner to identify
train a supervised learner to identify topical content 
\rev{from millions of features capturing content, user and social interactions on Twitter.}
\eat{over a large
feature space given a small set of seed hashtags as proxies for
topic labels.}  
On a corpus of approximately 1 billion English Tweets
% or 40TB of Twitter data?  does not seem like 1 billions tweets though!
collected from the Twitter
streaming API during 2013 and 2014 and learning for 10 diverse \rev{themes}\eat{topics}
ranging from social issues to celebrity deaths to the ``Iran nuclear
deal'', we empirically show that our learned social sensor
automatically generalizes to unseen future content 
\eat{(including content with no hashtags)}
with high ranking and precision scores.  Furthermore, 
we provide an extensive analysis of features and feature types across
different topics that reveals, for example, that (1)~largely
independent of topic, simple terms are the most informative feature
followed by location features and that (2)~the number of unique
hashtags and tweets by a user correlates more with their
informativeness than their follower or friend count.  In summary, this
work provides a novel, effective, and efficient way to learn topical
social sensors from a seed set of hashtags requiring minimal user
curation effort and offering strong generalization to future topical content.


%Twitter represents a massively distributed social sensor of a rich
%underlying topic space that drives its content generation.  Yet
%Twitter content is so diverse, decentralized, and dynamic in nature,
%that it is hard to automatically aggregate this topical content.  To
%address this need, we provide a novel way of learning topical social
%sensors on Twitter that learn from a provided set of topical hashtags
%and generalize to identify topical tweets with previously unseen tags.
%These learning social sensors leverage a variety of user-based,
%hashtag-based, term-based, and location-based features for
%distinguishing topical from non-topical tweets; we further analyze
%these features to understand which features are most useful and why.
%We further assess general global topical trends and how our learning
%sensors are able to follow these trends by drawing from a rich variety
%of sources on the Twittersphere to enable a first generation of
%learning social sensors for Twitter.
