%!TEX root = document.tex

\label{sec:introduction}

Social media sites such as Twitter present a double-edged sword for
users.  On one hand these sources contain a vast amount of novel and
topical content that challenge traditional news media sources in terms
of their timeliness and diversity.  Yet on the other hand they also
contain a vast amount of spam and otherwise low-value content for most
users' information needs where filtering out irrelevant content is
extremely time-consuming.  Hence, while it is widely acknowledged that
social media sources can be used as topical content sensors (indeed,
an entire European Union project was focused on ``Social Sensor''
research\footnote{\texttt{http://www.socialsensor.eu/}}.),
automatically learning high-precision sensors (i.e., ranking and
retrieval methods) for arbitrary topics that generalize to future
unseen content remains an open question in the literature and
comprises the key problem we seek to address in this paper.

Perhaps the critical bottleneck for learning targeted topical social
sensors is to achieve sufficient supervised content labeling; with
data requirements often in the thousands of labels to ensure effective
learning and generalization, manual labeling is simply too
time-consuming for many users and crowdsourced labels are both costly
and prone to misinterpretation of users' information needs.
Fortuitously, hashtags have emerged in recent years as a pervasive
topical proxy on social media sites --- hashtags originated on IRC
chat, were adopted later (and perhaps most famously) on Twitter, and
now appear on other microblogs (e.g., Sina and Tencent Weibo) and even
Facebook.  Hence as a simple enabling insight that serves as a
catalyst for effective topical social sensor learning, we leverage a
(small) set of user-curated topical hashtags to efficiently provide a
large number of supervised topic labels for social media content.

With the data labeling bottleneck resolved, we proceed to train
supervised classification and ranking methods to learn topical content
from a large feature space of source users and their locations, terms,
hashtags, and mentions.  On a corpus of approximately (choose one: 1
billion English Tweets / 40 TB of data) collected from the Twitter
streaming API during 2013 and 2014 and covering 10 diverse topics
ranging from social issues to celebrity deaths to the ``Iran nuclear
deal'', we empirically show that two simple and efficiently trainable
methods --- logistic regression and naive Bayes --- generalize well to
unseen future topical content (including content with no hashtags) in
terms of their mean average precision (MAP) and Precision@$n$ for a
range of $n$.  Furthermore, we show that terms and locations are among
the most useful features --- surprisingly more so than hashtags, even
though hashtags were used to label the data!  And perhaps even more
surprisingly, the number of unique hashtags and tweets by a user
correlates more with their informativeness than their follower or
friend count.
%Overall, our feature analysis indicates that the most
%useful features are sometimes counter-intuitive and that in general
%learning methods may be much more effective than manual engineering
%for building topical social sensors.

In summary, this work fills a major gap in the literature of topical
social sensors and how to effectively and efficiently learn them given
minimal supervision from a user.  Our results suggest that these
sensors generalize well to unseen future topical content and provide a
novel paradigm for the extraction of high-value content from social
media.

%Twitter hosts lots of information, on average more than $2,200$ new tweets every second. This can get up to $3$ to $4$ times increase during large events such as tsunami. \footnote{\hyperref[]{https://blog.twitter.com/2011/the-engineering-behind-twitter-s-new-search-experience}}
%\begin{itemize}
%\item Twitter is a vast sensor of content generated by latent phenonema (e.g., flu, political sentiment, elections, environment).
%\item Learning topical social sensors (politicians in NY, road conditions in Toronto) -- very broad topics for which its hard to manually specify a useful query.
%\item But there is interesting topical content and wouldn't it be cool if we could learn a social sensor for a targeted topic?
%\item Key insight is that hashtags are topical and can be used to bootstrap a supervised learning system that as we will show generalizes well beyond the seed hashtags.
%\item Conclusion is a new way to build topical real-time feeds that are otherwise difficult to do with existing Twitter tools (???).
%\end{itemize}
%section{Learning Topical Social Sensors}

%Start off with the questions that we want to answer in this section:
%
%- How to evaluate, labeling (problem of no supervised labels for tweets, indirect via hashtags as topical surrogates, leads to question of hashtag curation)?
%
%- Which classification algorithm is best / most robust for learning topical social sensors?
